\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{hyperref}

\begin{document}
\begin{titlepage}
\centering

{\Large\bfseries Unpacking Interpretability: Human-Centered Criteria for Optimal Combinatorial Solutions\par}
\vspace{1.5cm}

{\large
Dominik Pegler\textsuperscript{1,2},
Frank Jäkel\textsuperscript{2},
David Steyrl\textsuperscript{1},
Frank Scharnowski\textsuperscript{1}, \& 
Filip Melinscak\textsuperscript{1}\par
}

\vspace{1cm}

\raggedright
\textsuperscript{1} Department of Cognition, Emotion, and Methods in Psychology, Faculty of Psychology, University of Vienna, Austria\\
\textsuperscript{2} Centre for Cognitive Science \& Institute of Psychology, TU Darmstadt, Germany

\vspace{1cm}

\textbf{Corresponding author}: Dominik Pegler. Email: \texttt{dominik.pegler@univie.ac.at}

\vspace{0.5cm}

\textbf{Funding}: This research was funded by the Austrian Research Promotion Agency (FFG), Project Nos. 471030, 887474, and 927913. D.P. was funded by the Austrian Federal Ministry for Women, Science and Research (BMFWF) via the OeAD [MPC-2025-04543]. F.M. was funded by the Austrian Science Fund (FWF) [10.55776/ESP133].

\vspace{0.5cm}

\textbf{Declaration of competing interests}: The authors declare no competing interests.

\vspace{0.5cm}

\textbf{Acknowledgments}: We would like to thank Rita Hansl, Alex Karner, Kathrin Kostorz, Cindy Lor, Daniel Reiter, Annika Trapple, Nicole Wimmer, and Mengfan Zhang for their contributions during the development of the web-based experiment. We thank Hermann Kaindl for helpful discussions and feedback during the development of this research.

\vspace{0.5cm}

\textbf{CRediT author statement}: D.P.: Conceptualization, Investigation, Methodology, Software, Formal Analysis, Data Curation, Visualization, Writing -- Original Draft, Writing -- Review \& Editing. F.J.: Methodology, Writing -- Review \& Editing. D.S.: Writing -- Review \& Editing. F.S.: Resources, Supervision, Writing -- Review \& Editing. F.M.: Supervision, Conceptualization, Investigation, Methodology, Software, Writing -- Original Draft, Writing -- Review \& Editing.

\vspace{0.5cm}

\textbf{Data availability}: The code, materials, and data used in this research are publicly available at: \url{https://osf.io/4wjgp}

\vfill
\end{titlepage}
\end{document}
